Higgs Assisted Razor Search for Higgsinos at a 100 TeV $pp$ Collider

### 2019-10-21 referee_reply/referee_reply.tex

\reply{} We have corrected the sentence to state that the
limits on electroweakinos are between 0.15 and 1.0 TeV, depending on the mixing
of the gauge eigenstates.

\issue{3} On page 2 the authors write The most interesting
regions of split SUSY....  This is a biased statement. Interesting because of
exactly what reason? The most interesting for who, and why? Please explain
and/or clarify.

\reply{} We acknowledge that this statement is too
strong, and have accordingly softened it, clarifying that our main interest is
in discovering thermal electroweakino dark matter.

\issue{4} On page 3 the authors make a brief overview of existing bounds on
electroweakinos at 100 TeV colliders, and a few important references are
missing. On one hand, the studies going for ``small mass splittings"
[23,25,31,32] strongly drew inspiration from the mono-jet + soft-lepton
strategies (dubbed ``soft-lepton search" by the authors) that were proposed and
studied for the LHC in e.g: 1004.4902, 1307.5952, 1310.4274, 1312.7350,
1401.1162, 1401.1235, etc. Furthermore, bounds are quoted on Winos including
disappearing track searches but not on Higgsinos (1703.05327, 1703.09675,
1901.02987 should be added), nei- ther acknowledging the chance that Higgsinos
below 100 GeV can still occur (1801.05432). This is a strange choice given that
the authors work in a Bino-Higgsino system.

\reply{} We have added the references to the earlier studies proposed for the
LHC.

### 2019-10-21 main.tex
Adding references to earlier studies of mono-jet and soft-lepton channels for the LHC

The optimal search strategy for finding electroweakinos   highly depends on
their mass spectra \cite{Han:2013kza}.  Phenomenological collider studies on
finding electroweakinos with a small mass splitting of about 0.1 $-$ 50 GeV at a
100 TeV $pp$  collider can be found in \cite{Low:2014cba, Bramante:2014tba,
Berlin:2015aba, Cirelli:2014dsa}.
For $3\ \text{ab}^{-1}$ of data, the projected exclusion reaches for pure Wino
LSPs using the monojet channel is about $1.4$~TeV.  The reach
can be increased to $\sim3$ TeV with a disappearing tracks search.
Neutralinos up to 1 TeV can be excluded for mass splittings of about 20-30 GeV,
using a soft lepton search \cite{Low:2014cba}. Additionally, Bino-Wino LSPs
with masses up to 1.5 TeV for an inter-state mass splitting of around 1 GeV  can be
discovered at a 100 TeV $pp$ collider with $\sim7\ \text{ab}^{-1}$
of data \cite{Bramante:2014tba}.

>>>>

The optimal search strategy for finding electroweakinos is highly dependent on
their mass spectra \cite{Han:2013kza}. Phenomenological collider studies on
finding electroweakinos with a small mass splitting of about 0.1 $-$ 50 GeV at a
100 TeV $pp$  collider can be found in \cite{Low:2014cba, Bramante:2014tba,
Berlin:2015aba, Cirelli:2014dsa}, which in turn draw inspiration from earlier
studies done for the LHC \cite{Giudice:2010wb, Gori:2013ala, Han:2013usa,
Schwaller:2013baa, Baer:2014cua, Han:2014kaa}.
For $3\ \text{ab}^{-1}$ of data, the projected exclusion reaches for pure Wino
LSPs using the monojet channel is about $1.4$~TeV.  The reach
can be increased to $\sim3$ TeV with a disappearing tracks search.
Neutralinos up to 1 TeV can be excluded for mass splittings of about 20-30 GeV,
using a soft lepton search \cite{Low:2014cba}. Additionally, Bino-Wino LSPs
with masses up to 1.5 TeV for an inter-state mass splitting of around 1 GeV  can be
discovered at a 100 TeV $pp$ collider with $\sim7\ \text{ab}^{-1}$
of data \cite{Bramante:2014tba}.
